Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-05-08 tex/VHzQ.tex
VHzQ.tex update

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                           
%%  
%%									    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[usenatbib]{mnras}

@@

\iffalse
\section*{TO DOs}
{\bf For NPR: }
\begin{itemize}
\item Concentrate on reporting NIR and W1/W2 figures and tables
\item SED dust plots 
\item Filter curve plot with LSST, Euclid and even wide JWST filters...; 
\item Check for NIR and MIR variabilty with the Wu quasar
\item Check with SpIES/SHELA (but only 3.4/4.6$\mu$m; 
%%\item Almost certainly want to compile M$_{\rm BH}$; THIS CAN WAIT, otherwise is massive paper-creep
%%\item May well wanna try and get M$_{\star}$ too...!! (yuck); THIS CAN WAIT, otherwise is massive paper-creep
\end{itemize}

\noindent
{\bf For NJGC: }
\begin{itemize}
\item Write the NIR data section(s) 
\end{itemize}

\noindent
{\bf For Both: }
\begin{itemize}
\item Need to decide what mags and mag system we are reporting, especially in the 
NIR...
\item Depth/area QLF calculation to see whether the NIR surveys have been fully mined...
\item Question from Sarah Bosman:: are the $y$-magnitudes AB? They seem all quite a bit brighter than the ones given in Banados+16. Do you know why that is?
\end{itemize}
\fi

@@

We have compiled a list of 463 quasars with redshifts $z\geq5.00$. We use all the $z\geq5.00$ quasars that have been discovered, spectroscopically confirmed and published as of 2018-Dec-31. We then obtain optical, near-infrared and mid-infrared photometry for the spectral dataset. The optical data comes from the Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) survey \citep{Chambers2016}. The near-infrared data comes from two sources: first, the WFCAM \citep[][]{Casali2007} on the UKIRT, primarly, but not exclusively, as part of the UKIRT Infrared Deep Sky Survey \citep[UKIDSS; ][]{Lawrence2007}.  And second, data from the VIRCAM on the VISTA \citep[][]{Emerson2006, Dalton2006}. The mid-infrared, $\lambda=3-30\mu$m wavelength data is from the the Wide-Field Infrared Survey Explorer \citep[WISE;][]{Wright2010, Cutri2013} mission. 
%%
For reference, Figure~\ref{fig:filters} displays the wavelength and normalised transmission of the filters in question.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                           
%%   The `compliation' paper for all z>5 spec-z quasars, here called "Very High Redshift Quasars" (VHzQs) and 
%%   looking into their IR properties. Motivations include putting a list of all the VHzQ in one place, looking for 
%%   signs of super-critical accretion and having a super-set of objects and their given parameters ahead of 
%%   JWST GO Cycle 1. 
%%									    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[usenatbib]{mnras}

@@

@@

We have compiled a list of 463 quasars with redshifts $z\geq5.00$. We use all the $z\geq5.00$ quasars that have been discovered, spectroscopically confirmed and published as of 2018 December 31 (MJD 58483). We then obtain optical, near-infrared and mid-infrared photometry for the spectral dataset. The optical data comes from the Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) survey \citep{Chambers2016}. The near-infrared data comes from two sources: first, the WFCAM \citep[][]{Casali2007} on the UKIRT, primarly, but not exclusively, as part of the UKIRT Infrared Deep Sky Survey \citep[UKIDSS; ][]{Lawrence2007}.  And second, data from the VIRCAM on the VISTA \citep[][]{Emerson2006, Dalton2006}. The mid-infrared, $\lambda=3-30\mu$m wavelength data is from the the Wide-Field Infrared Survey Explorer \citep[WISE;][]{Wright2010, Cutri2013} mission. For reference, Figure~\ref{fig:filters} displays the wavelength and normalised transmission of the filters in question.
